%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% Website: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      %Change to \textit for italicized subheadings
      \text{\small#3} & \text{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Shreyas V. Srinivasan} & Email: \href{mailto:shreyass@mit.edu}{shreyass@mit.edu}\\
  Website: \href{http://shreyas.finance}{shreyas.finance} & LinkedIn: \href{https://www.linkedin.com/in/svsrinivasan/}{in/svsrinivasan}\\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {MIT Sloan School of Management}{Cambridge, MA}
      {MFin, Financial Engineering}{2021 - 2022}
        \resumeItemListStart
            \resumeItem{Activities \& Societies}
            {Quantitative Financial Markets Club, MFin Capital Builders}
        \resumeItemListEnd
    \resumeSubheading
      {Massachusetts Institute of Technology (MIT)}{Cambridge, MA}
      {SB, Mathematics with Computer Science (Minor: Finance); GPA: 4.8/5.0}{2018 - 2021}
        \resumeItemListStart
            \resumeItem{Activities \& Societies}
            {MIT Pokerbots, MIT Consulting Group, Phi Kappa Theta Fraternity}
            \resumeItem{Selected Coursework}
            {15.457 Advanced Analytics of Finance (Grad), 15.438 Fixed Income Securities \& Derivatives (Grad),\qquad6.046 Algorithms, 18.100Q Real Analysis, 18.650 Statistics, 18.600 Probability, 6.036 Machine Learning, 18.03 ODEs}
        \resumeItemListEnd
    \resumeSubheading
      {Princeton University}{Princeton, NJ}
      {Dual Enrollment, Mathematics; GPA: 3.7/4.0; Courses: Honors Linear Algebra, Number Theory}{2017 - 2018}
    % \resumeSubheading
    %   {West Windsor--Plainsboro High School South}{Princeton Jct., NJ}
    %   {High School Diploma; GPA: 4.0/4.0; ACT: 36/36; National Merit Scholar}{2014 - 2018}
  \resumeSubHeadingListEnd


%-----------WORK EXPERIENCE-----------------
\section{Work Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {DRW}{Greenwich, CT}
      {Quantitative Trading Analyst Intern}{Jun - Aug 2021}
      \resumeItemListStart
        \resumeItem{Project}
          {quantitative analysis in the U.S. Treasury futures and options markets.}
      \resumeItemListEnd
    \resumeSubheading
      {Morgan Stanley}{New York, NY}
      %Summer Analyst -- Equity Derivatives Trading \& Structuring
      {Institutional Equity Summer Analyst}{Jun - Aug 2020}
      \resumeItemListStart
        \resumeItem{Projects}
          {Implemented ETF trading strategy and binary classifier for dynamic option Gamma hedging in Python.}
        \resumeItem{Shadowing}
          {Index Derivatives, Single Name Options, ETFs, and Automated Market Making trading desks.}
        \resumeItem{Skills}
          {Derivatives pricing, option Greeks, option strategies, and quantitative risk management.}
      \resumeItemListEnd
    
    \resumeSubheading
      {Seven Eight Capital}{New York, NY}
      {Quantitative Developer Intern}{May - Aug 2019}
      \resumeItemListStart
        \resumeItem{Project}
          {Built, studied, and evaluated multi-factor asset pricing models for US and European equities.}
        \resumeItem{Skills}
          {Python (Pandas), data science (regression analysis, model selection, outliers), and BARRA risk models.}
      \resumeItemListEnd
  
    % \resumeSubheading
    %   {Fish \& Richardson P.C.}{Boston, MA}
    %   {Patent Prosecution Intern}{Jan - Mar 2019}
    %   \resumeItemListStart
    %     \resumeItem{Drafting}
    %       {Patent applications, responses to US/foreign patent office rejections, and client IP portfolio analyses.}
    %     \resumeItem{Skills}
    %       {Technology analysis, product differentiation, science communication, and argument construction.}
    %   \resumeItemListEnd

  \resumeSubHeadingListEnd
  

%-----------WORK EXPERIENCE-----------------
\section{Research Experience}
  \resumeSubHeadingListStart
    
      \resumeSubheading
      {MIT Sloan School of Management}{Cambridge, MA}
      {Undergraduate Research Assistant -- Operations Research \& Statistics Group}{Feb 2021 - May 2021}
      \resumeItemListStart
        \resumeItem{Project}
          {Analyzed the applications of Markov Chains to real-world systems to investigate forecastability.}
        \resumeItem{Skills}
          {Julia, Optimization, Linear Programming.}
      \resumeItemListEnd
  
      \resumeSubheading
      {MIT Sloan School of Management}{Cambridge, MA}
      {Undergraduate Research Assistant -- Accounting Group}{May 2020 - May 2021}
      \resumeItemListStart
        \resumeItem{Project}
          {Evaluated and compared methodologies for calculating single name expected stock returns.}
        \resumeItem{Skills}
          {Quantitative modeling in R, big data practices, and numerical optimization techniques.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
      
      
%-----------LEADERSHIP EXPERIENCE-----------------
\section{Extracurricular Experience}
  \resumeSubHeadingListStart
    
    \resumeSubheading
      {MIT Pokerbots}{Cambridge, MA}
      {President (2019 - 2021), Sponsorship Director (2018 - 2019)}{Sep 2018 - Present}
      \resumeItemListStart
        \resumeItem{President}
          {Led team of seven members to successfully run four-week computer poker class and competition for 250 MIT undergrad/grad students. Managed operations, coordinated with MIT/EECS department, and developed 2021 game engine.}
      \resumeItemListEnd
  
    \resumeSubheading
      {MIT Consulting Group}{Cambridge, MA}
      {Corporate Relations Director (2020), Secretary (2019)}{Sep 2018 - May 2021}
      \resumeItemListStart
        \resumeItem{Consultant}
          {Produced strategy recommendations for companies ranging from startup to Fortune 500 in scale. Gained experience in conducting market research, identifying growth opportunities, and creating strategic partnerships.}
      \resumeItemListEnd
      
    % \resumeSubheading
    %   {Phi Kappa Theta Fraternity}{Boston, MA}
    %   {Rush Chair (2020 - Present), Social Chair (2019)}{Sept 2018 - Present}
    %   \resumeItemListStart
    %     \resumeItem{Rush Chair}
    %       {Responsible for recruiting new members, planning events, and overseeing budget of \$25,000.}
    %   \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------AWARDS-----------------
\section{Awards}
  \resumeSubHeadingListStart
    \resumeSubItem{MIT MFin Fellowship}
        {Awarded in recognition of outstanding academic record, achievements and professional promise.}
    \resumeSubItem{Young Naturalist Awards Research Competition}
      {Individually top 6 nationwide for biology research.}
    \resumeSubItem{Olympiads}
      {2 time AIME qualifier, USACO Gold Division.}
     \resumeSubItem{Tournament of Champions}
      {Two time qualifier in Public Forum Debate (national high school championships).}
    % \resumeSubItem{National Speech \& Debate Association}
    %   {2\textsuperscript{nd} in NJ for Mock Trial during senior year of high school.}
    % \resumeSubItem{New Jersey Governor's School in the Sciences Scholar}
    %   {Summer research program for top 50 NJ rising high school seniors in the sciences. Conducted research in machine learning (document classification).}


  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Skills \& Interests}
 \resumeSubHeadingListStart
   \item{
   	Python, R, Java, MATLAB, Julia, Data Science, Public Speaking, Science Communication, Leadership
   }
  \item{
    DJing, Basketball, Racquetball, Cricket, Debate, Public Policy, Traveling
  }
 \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
